A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
Precised the provenance

\begin{lstlisting}[caption={Using \c{eval} and \c{parse} to do meta-programming in package \emph{data.table}, to build the options at load time.}, label=code:parsepaste]
eval(parse(text=paste0("options(",i,"=",opts[i],")")))
\end{lstlisting}

>>>>

\begin{lstlisting}[caption={Using \c{eval} and \c{parse} to do meta-programming in package \emph{data.table}, to build the options at load time (in \emph{onLoad.R}).}, label=code:parsepaste]
eval(parse(text=paste0("options(",i,"=",opts[i],")")))
\end{lstlisting}

\textbf{What about a table of packages ranked by usage of parse (and/or paste...)?}
